\textls[-0]{\thetitle}

### 2023-03-04 challenge.tex
tweak
shortening in §1–2

Integrating family polymorphism into a proof assistant presents challenges
far beyond those found in an object-oriented setting~\cite{ncm2004,vc-calculus-2006,zm2017},
because the underlying programming language is simultaneously
functional, dependently typed, a logic, and an interactive tool.

@@

However, there is a tension between extensibility of inductive types
and exhaustivity of induction reasoning.\footnote{%
The tension reflects a duality between variants and records.
For record-like language constructs (e.g., classes and objects), it is
safe for an extension to add more fields: existing fields can still be
projected.
But variant-like constructs (e.g., inductive types) do not automatically
enjoy safe, modular addition of constructors:
existing pattern matches could potentially become non-exhaustive.}
In \cref{fig:stlc-nonmechanized}, all the lemmas and theorems, as well as
the substitution function, require induction (i.e., elimination of inductive types).
A language design must enforce that induction remains exhaustive in the
face of the new constructors in the derived family.
For modularity, the type system should do so without requiring
redefinition or rechecking of those cases already handled by the base
family.

@@

Interactive theorem proving and tactic programming are central to
a typical programming experience with a proof assistant.
A language design integrating family polymorphism should be compatible
with these forms of programming.
In particular, it should be possible in our system to
incrementally navigate through vernacular commands and, moreover, construct proofs
with common tactics while getting instant feedback on the proof state,
even in the middle of a family definition.
Last but not least, in addition to producing theorems,
it should be possible for terms defined in families to possess computational content.

>>>>

Integrating family polymorphism into a proof assistant presents challenges
far beyond those found in an object-oriented setting, %\cite{ncm2004,vc-calculus-2006,zm2017},
as the underlying programming language is simultaneously
functional, dependently typed, a logic, and an interactive tool.

@@

However, there is a tension between extensibility of inductive types
and exhaustivity of induction reasoning.\footnote{%
The tension reflects a duality between variants and records.
With record-like language constructs (e.g., OO classes),
it is safe for an extension to add new fields:
existing fields can still be projected.
But variant-like constructs (e.g., inductive types) do not automatically
enjoy safe, modular addition of constructors:
existing pattern matches could become non-exhaustive.}
In \cref{fig:stlc-nonmechanized}, all the lemmas and theorems, as well as
the substitution function, require induction (i.e., elimination of inductive types).
A language design must enforce that induction remains exhaustive in the
face of the new constructors in the derived family.
For modularity, the type system should do so without requiring
redefinition or rechecking of those cases already handled by the base
family.

@@

Interactive theorem proving and tactic programming are central to
a typical programming experience with a proof assistant.
A language design integrating family polymorphism should be compatible
with these forms of programming.
In particular, it should be possible in our system to
incrementally navigate through vernacular commands and, moreover, construct proofs
with common tactics while getting instant feedback on the proof state,
even in the middle of a family definition.
Last but not least, in addition to proving theorems,
it should be possible for terms defined with families to possess computational content.
